parental migration and adolescents educational performance

### 2022-05-28 data/Gu-thesis-script.Rmd
control var: num of siblings

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         is.girl = if_else(a01 == 2, 1, 0), #student is girl
         is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
         is.only.child = if_else(b01 == 1, 1, 0), #student is only child
         is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
         #fa.edu = b07,
         #mo.edu = b06,
         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.book = b12 #Amount of book at home, student self-rated 
) %>% drop_na(
  is.girl, is.rural, is.only.child, is.boarding, par.edu, home.internet, home.book)
```

@@

## Descriptive statistics
```{r}
des_gender <- d_cl %>% count(is.girl)
des_rural <- d_cl %>% count(is.rural)
des_only.child <- d_cl %>% count(is.only.child)
des_boarding <- d_cl %>% count(is.boarding)
des_book <- d_cl %>% group_by(home.book) %>% count
des_internet <- d_cl %>% group_by(home.internet) %>% count
des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
des_gender
des_rural
des_only.child
des_boarding
des_par.edu.year
des_book
des_internet
```

@@

Results
```{r}
models_cog <- list(
did_cog,
did_cog_m_only,
did_cog_m,
did_cog_f,
did_cog_f_only,
did_cog_both) 
models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_ttl <- list(
did_ttl,
did_ttl_m_only,
did_ttl_m,
did_ttl_f,
did_ttl_f_only,
did_ttl_both) 
models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_chn <- list(
did_chn,
did_chn_m_only,
did_chn_m,
did_chn_f,
did_chn_f_only,
did_chn_both) 
models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_mat <- list(
did_mat,
did_mat_m_only,
did_mat_m,
did_mat_f,
did_mat_f_only,
did_mat_both) 
models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_eng <- list(
did_eng,
did_eng_m_only,
did_eng_m,
did_eng_f,
did_eng_f_only,
did_eng_both) 
models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_unres_cog <- list(
did_unres_cog,
did_unres_cog_m_only,
did_unres_cog_m,
did_unres_cog_f,
did_unres_cog_f_only,
did_unres_cog_both) 
models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_unres_ttl <- list(
did_unres_ttl,
did_unres_ttl_m_only,
did_unres_ttl_m,
did_unres_ttl_f,
did_unres_ttl_f_only,
did_unres_ttl_both) 
models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_unres_chn <- list(
did_unres_chn,
did_unres_chn_m_only,
did_unres_chn_m,
did_unres_chn_f,
did_unres_chn_f_only,
did_unres_chn_both) 
models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_unres_mat <- list(
did_unres_mat,
did_unres_mat_m_only,
did_unres_mat_m,
did_unres_mat_f,
did_unres_mat_f_only,
did_unres_mat_both) 
models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Results
```{r}
models_unres_eng <- list(
did_unres_eng,
did_unres_eng_m_only,
did_unres_eng_m,
did_unres_eng_f,
did_unres_eng_f_only,
did_unres_eng_both) 
models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_cog <- list(
did_adj_cog,
did_adj_cog_m_only,
did_adj_cog_m,
did_adj_cog_f,
did_adj_cog_f_only,
did_adj_cog_both) 
models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on total exam score
```{r}
did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_ttl <- list(
did_adj_ttl,
did_adj_ttl_m_only,
did_adj_ttl_m,
did_adj_ttl_f,
did_adj_ttl_f_only,
did_adj_ttl_both) 
models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Chinese exam score
```{r}
did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_chn <- list(
did_adj_chn,
did_adj_chn_m_only,
did_adj_chn_m,
did_adj_chn_f,
did_adj_chn_f_only,
did_adj_chn_both) 
models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Math score
```{r}
did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_mat <- list(
did_adj_mat,
did_adj_mat_m_only,
did_adj_mat_m,
did_adj_mat_f,
did_adj_mat_f_only,
did_adj_mat_both) 
models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on English score
```{r}
did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_eng <- list(
did_adj_eng,
did_adj_eng_m_only,
did_adj_eng_m,
did_adj_eng_f,
did_adj_eng_f_only,
did_adj_eng_both) 
models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
did_adj_unres_cog,
did_adj_unres_cog_m_only,
did_adj_unres_cog_m,
did_adj_unres_cog_f,
did_adj_unres_cog_f_only,
did_adj_unres_cog_both) 
models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

>>>>

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         is.girl = if_else(a01 == 2, 1, 0), #student is girl
         is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
         #is.only.child = if_else(b01 == 1, 1, 0), #student is only child
         is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
         is.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
         #fa.edu = b07,
         #mo.edu = b06,
         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.book = b12 #Amount of book at home, student self-rated 
) %>% drop_na(
  is.girl, is.rural, is.boarding, is.ethn.minority, par.edu, home.internet, home.book)
```

```{r}
d_cl <- d_cl %>% mutate_at(c('b0201', 'b0202', 'b0203', 'b0204'), ~replace(., is.na(.), 0))
d_cl <- d_cl %>% mutate(sibling = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204)) %>% #number of siblings
  drop_na(sibling)
```

@@

## Descriptive statistics
```{r}
des_gender <- d_cl %>% count(is.girl)
des_rural <- d_cl %>% count(is.rural)
des_sibling <- d_cl %>% group_by(sibling) %>% count
des_boarding <- d_cl %>% count(is.boarding)
des_book <- d_cl %>% group_by(home.book) %>% count
des_internet <- d_cl %>% group_by(home.internet) %>% count
des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
des_ethn.minority <- d_cl %>% group_by(is.ethn.minority) %>% count
des_gender
des_rural
des_sibling
des_boarding
des_par.edu.year
des_book
des_internet
des_ethn.minority
```

@@

Results
```{r}
models_cog <- list(
did_cog,
did_cog_m_only,
did_cog_m,
did_cog_f_only,
did_cog_f,
did_cog_both) 
models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_ttl <- list(
did_ttl,
did_ttl_m_only,
did_ttl_m,
did_ttl_f_only,
did_ttl_f,
did_ttl_both) 
models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_chn <- list(
did_chn,
did_chn_m_only,
did_chn_m,
did_chn_f_only,
did_chn_f,
did_chn_both) 
models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_mat <- list(
did_mat,
did_mat_m_only,
did_mat_m,
did_mat_f_only,
did_mat_f,
did_mat_both) 
models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_eng <- list(
did_eng,
did_eng_m_only,
did_eng_m,
did_eng_f_only,
did_eng_f,
did_eng_both) 
models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_unres_cog <- list(
did_unres_cog,
did_unres_cog_m_only,
did_unres_cog_m,
did_unres_cog_f_only,
did_unres_cog_f,
did_unres_cog_both) 
models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_unres_ttl <- list(
did_unres_ttl,
did_unres_ttl_m_only,
did_unres_ttl_m,
did_unres_ttl_f_only,
did_unres_ttl_f,
did_unres_ttl_both) 
models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_unres_chn <- list(
did_unres_chn,
did_unres_chn_m_only,
did_unres_chn_m,
did_unres_chn_f_only,
did_unres_chn_f,
did_unres_chn_both) 
models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_unres_mat <- list(
did_unres_mat,
did_unres_mat_m_only,
did_unres_mat_m,
did_unres_mat_f_only,
did_unres_mat_f,
did_unres_mat_both) 
models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Results
```{r}
models_unres_eng <- list(
did_unres_eng,
did_unres_eng_m_only,
did_unres_eng_m,
did_unres_eng_f_only,
did_unres_eng_f,
did_unres_eng_both) 
models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_cog <- list(
did_adj_cog,
did_adj_cog_m_only,
did_adj_cog_m,
did_adj_cog_f_only,
did_adj_cog_f,
did_adj_cog_both) 
models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on total exam score
```{r}
did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_ttl <- list(
did_adj_ttl,
did_adj_ttl_m_only,
did_adj_ttl_m,
did_adj_ttl_f_only,
did_adj_ttl_f,
did_adj_ttl_both) 
models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_chn <- list(
did_adj_chn,
did_adj_chn_m_only,
did_adj_chn_m,
did_adj_chn_f_only,
did_adj_chn_f,
did_adj_chn_both) 
models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Math score
```{r}
did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_mat <- list(
did_adj_mat,
did_adj_mat_m_only,
did_adj_mat_m,
did_adj_mat_f_only,
did_adj_mat_f,
did_adj_mat_both) 
models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on English score
```{r}
did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_eng <- list(
did_adj_eng,
did_adj_eng_m_only,
did_adj_eng_m,
did_adj_eng_f_only,
did_adj_eng_f,
did_adj_eng_both) 
models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
did_adj_unres_cog,
did_adj_unres_cog_m_only,
did_adj_unres_cog_m,
did_adj_unres_cog_f_only,
did_adj_unres_cog_f,
did_adj_unres_cog_both) 
models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_f,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```
